USAGE: 

1) First, run each of the code chunk from top to bottom. Next, run just the last code chunk to get the plots.
2) Make sure you have the correct Path name and file name in the 2nd code chunk (line 19-28)
3) In the 4th code chunk, you can change holiday_var to "USIndependenceDay", "ChristmasDay", "USLaborDay" (line ~ 51)
4) In the 6th code chunk, you can tweak the "days_before_holiday" and "days_after_holiday" variables (line ~ 102-103)
5) In the 7th code chunk, you can set "case" to equal 1 for ON, 2 for 1 week, 3 for 4 weeks. (line ~ 117)
```{r}
# Load Libraries
library(lubridate)
library(dplyr)
library(ggplot2)
library(plotly)
library(timeDate)
```

```{r}
PATH = "/Users/anthonynguyen/Desktop/IMA_bootcamp/Week_4/LIBOR_RATES/July_17/"

# Name of your file dot extension (e.g. LIBOR_USD.csv)
FILENAME = "LIBOR_USD.csv"

# Concatenate PATH and FILENAME strings
File_Path = paste(PATH,FILENAME,sep="")

# READ in CSV and name it "DATA"
DATA <- read.csv(File_Path)
```

```{r}
##############################################################################
# Create a new table named "rates_to_track" from "LIBOR" with column name "time stamp" containing entries with format Year-Month-Day 
##############################################################################
rates_to_track <- DATA

# Convert date format to year-month-day
rates_to_track <- rates_to_track  %>% mutate(timestamp = as.Date(dmy(rates_to_track$Date)))  
##############################################################################

```

```{r}
##############################################################################

# listHolidays() will give you a list of possible holidays to use
# In this case, we're using ChristmasDay

# Examples: "USIndependenceDay", "ChristmasDay", "USLaborDay"

holiday_var = "ChristmasDay"
holidays <- c(holiday_var)  
Year_begin = 2003
Year_end = 2019

#https://stackoverflow.com/questions/41825688/loop-over-holidays-in-timedate-package

# Create a Table named "holiday_dates" line 59-63
  
# Holiday        | Date 
# ChristmasDay     2003-12-25
# ChristmasDay     2004-12-25
# ............     ..........
# ChristmasDay     2009-12-25 

holiday_dates = do.call(rbind,
        lapply(holidays, function(i){
          foo <- match.fun(i)  
          data.frame(Holiday = i,
                     Date = as.Date(foo(Year_begin:Year_end)))
        }))
#############################################################################
```

```{r}
# A function that finds how far a date is from the given holiday (the minimum distance). returns a column of this distance and the year of the holiday

close_to_holiday <- function(input_date){
  distance_from_all_holidays <- mutate(holiday_dates, relative_date = floor(as.period(interval(Date, input_date) ) %/% days(1) ) )%>%
    mutate(absolute_relative_date = abs(relative_date)) %>% arrange(absolute_relative_date)
  return(c(distance_from_all_holidays[1, "relative_date"], year(distance_from_all_holidays[1, "Date"])))
}

#############################################################################
```

```{r message=FALSE}

# next two functions are a hack to make the dataframe wrangling work, can be made better 
get_relative_date <- function(input_date){
  return(close_to_holiday(input_date)[1])
}

get_relative_holiday_year <- function(input_date){
  return(close_to_holiday(input_date)[2])
}

#############################################################################

# Specify how many days before holiday and how many after

days_before_holiday <- 10
days_after_holiday <- 15

# Finally, add relative holiday data to the dataframe and filter for the days you need 

rates_to_track_with_holiday_data <- rates_to_track %>% mutate(relative_date = lapply(timestamp, get_relative_date) ) %>% mutate(holiday_year = lapply(timestamp, get_relative_holiday_year)) %>%
  filter(relative_date >= days_before_holiday * -1 & relative_date <= days_after_holiday)

```

```{r}
# Creates vector Years_array = ("2004", "2005",...,"2018")
Years_array <- paste(c(2004:2018))
Number_of_Years <- length(Years_array)
# Switch: 1 (ON), 2 (1 Week), 3 (4 weeks)
case <- 1
# Create Heaviside function for data wrangling
Heaviside <- function(x,a = 0){if(x==0){return(0)} else{return((sign(x)+1)/2)}}

# Function performs regression on a given year in "holiday_data"
linear_regression <- function(year,holiday_data,case){
  
  holiday_data <- holiday_data %>% filter(as.double(holiday_year) == as.double(year))
  return(lm(switch(case,ON,X1W,X1M) ~ Week.day,data = holiday_data))}

# Function filter data in "holiday_data" in a given year
filtered_data <- function(year,holiday_data){
  holiday_data <- holiday_data %>% filter(as.double(holiday_year) == as.double(year))
  return(holiday_data)}

# Vector of intercepts beta_0's
vector_intercept = c()
for(j in c(1:Number_of_Years)){
  vector_intercept[j] = coef(linear_regression(Years_array[j],rates_to_track_with_holiday_data,case))[1]
}

# Vector of tabular data from year 2004-2019
vector_data_table = c()
for(j in c(1:Number_of_Years)){
  vector_data_table[[j]] <- filtered_data(Years_array[j],rates_to_track_with_holiday_data)
}

# Add columns which includes recentered rates and Pre column
for(j in c(1:Number_of_Years)){
  vector_data_table[[j]] <- vector_data_table[[j]] %>% mutate(recentered_rates = switch(case,ON,X1W,X1M) - vector_intercept[j]) %>% mutate(Pre = lapply(vector_data_table[[j]]$relative_date,Heaviside))
}

# Concatenate my tabular data from each year
largeData <- vector_data_table[[1]]
for(j in c(2:Number_of_Years)){
  largeData <- rbind(largeData,vector_data_table[[j]])
}

# Construct linear regrerssion model 
# recentered_rates (response), relative_date (predictor), Pre (binary categorical predictor)

model_recentered <- lm(recentered_rates ~ as.integer(Pre), data = largeData)
summary(model_recentered)

model_recentered <- lm(recentered_rates ~ as.integer(relative_date) + as.integer(Pre), data = largeData)
summary(model_recentered)

# Scatter Plot of recentered_rates vs relative_date
ggplot(largeData) + geom_point(aes(x = as.numeric(relative_date), y = recentered_rates, color = holiday_year))

```